Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-14 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd

**RESUME HERE**
$Rt$ had a significantly negative response to $ln[TWI]$ across all drought years combined (Fig. **4**, Table S8-S9). 
The effect was also significant for 1977 and 1999 individually (Fig. **4**, Table S8).
When $Rt_{ARIMA}$ was used as the response variable, the effect was significant in 1977, and included in some of the top models in 1966 and 1999 (Table S9).
This negates the idea that trees in moist microsites would be less affected by drought. 
Nevertheless, we tested for a $ln[H] *ln[TWI]$ interaction, a negative sign of which could indicate that smaller trees (presumably with smaller rooting volume) are more susceptible to drought in drier microenvironments with a deeper water table. 
This hypothesis was rejected, as the $ln[H] *ln[TWI]$ interaction was never significant, and had a positive sign in any top models in which it appeared (Tables 1, S8-S9).
This term did appear with a positive coefficient in the best $Rt_{ARIMA}$ model for all years combined (Table S9), indicating that the negative effect of height on  $Rt$ was significantly stronger in wetter microhabitats.

>>>>

Trees in drier microsites showed greater growth declines during drought; i.e., $Rt$ had a significantly negative response to $ln[TWI]$ across all drought years combined, and in 1977 and 1999 individually (Fig. **4**, Table S8-S9). 
The $ln[H] *ln[TWI]$ interaction was never significant, and had a positive sign in any top $Rt$ models in which it appeared (Tables 1, S8-S9), rejecting the hypothesis that smaller trees (presumably with smaller rooting volume) are more susceptible to drought in microenvironments with a deeper water table. 
In contrast, $ln[TWI]$ did not appear in any of the best models for $Rc$ or $Rs$ (combined of for individual years), except in interaction with $ln[H]$ (Fig. 4, Tables S10-S11).
Negative $ln[H] *ln[TWI]$ interactions appeared in the best models for both $Rc$ and $Rs$ for all years combined, as well as in one individual year for each (1966 for $Rc$, 1977 for $Rs$). 
This implies that small trees had greater recovery and resilience in wetter microhabitats, whereas large trees had greater recovery and resilience in dry microhabitats.
